A Survey of Near-Term Exoskeleton Technology\\ (Draft 3.0)

### 2015-09-28 intent.tex
more updates

@@

>>>>

I have attached an Appendix with pointers to online behavior
recognition in related fields.

@@

\section{Appendix: Online Behavior Recognition}

\subsection{Review articles}

{\it 3D Gestural Interaction: The State of the Field,}
J. LaViola Jr.
\url{http://www.eecs.ucf.edu/~jjl/pubs/3dgesture.pdf}

\subsection{On-line (streaming) action recognition/detection in videos}

{\it Human Activity Prediction: Early Recognition of Ongoing Activities
from Streaming Videos,}
M. S. Ryoo
\url{http://michaelryoo.com/papers/iccv11_prediction_ryoo.pdf}

{\it Max-Margin Early Event Detectors,}
M. Hoai and F. De la Torre
\url{http://www.robots.ox.ac.uk/~minhhoai/papers/MMED_IJCV14.pdf}

\subsection{On-line (streaming) action recognition/detection using (Kinect) pose data}

{\it Exploring the Trade-off Between Accuracy and Observational Latency in
Action Recognition,}
C. Ellis, S. Z. Masood, M. Tappen, J. LaViola Jr., R. Sukthankar
\url{http://www.cs.ucf.edu/~mtappen/pubs/2012/ellis-et-al-ijcv-2012.pdf}

{\it The Moving Pose: An Efficient 3D Kinematic Descriptor for Low-Latency
Action Recognition and Detection,}
M. Zanfir, M. Leordeanu, C. Sminchisescu
\url{http://www.cv-foundation.org/openaccess/content_iccv_2013/papers/Zanfir_The_Moving_Pose_2013_ICCV_paper.pdf}

{\it Real-time Classification of Dance Gestures from Skeleton Animation,}
M. Raptis, D. Kirovski, H. Hoppe
\url{http://vision.ucla.edu/papers/raptisKH11.pdf}

\subsection{Accelerometer-based and other sensors}

{\it Activity Recognition on Streaming Sensor Data,}
N. Krishnan, D. Cook
\url{http://www.eecs.wsu.edu/~cook/pubs/pmc12.pdf}

{\it Macro-class Selection for Hierarchical kNN Classification of Inertial
Sensor Data,}
C. McCall, K. Reddy, M. Shah
\url{http://crcv.ucf.edu/papers/PECCS_2012.pdf}

{\it Audio-based Human Activity Recognition Using Non-Markovian Ensemble
Voting}
\url{http://www2.informatik.uni-freiburg.de/~spinello/storkROMAN12.pdf}

### 2015-09-28 technology.tex
more updates

\newcommand{\gc}{{\mbox {GravityCompensation}}}
\newcommand{\invdyn}{{\mbox {\tiny ID}}}

\newcommand{\shrinkfig}{\def\baselinestretch{1.0}\small} % 0.9 okay
\newcommand{\shrink}{\def\baselinestretch{1.1}\small} % 0.97 % 0.95 okay

@@

\title{A Survey of Near-Term Exoskeleton Technology\\
(Draft 2.1)}

@@

This paper surveys near-term exoskeleton technology with an
emphasis on control.
A companion paper surveys implemented exoskeleton technology~\cite{}.

@@

We do not survey exoskeleton technology for human arms. 
We treat the torso and helmet of the exoskeleton as the payload,
and focus on a lower body exoskeleton to support any payloads that
are on the torso or head.
We do not cover global energy storage such as batteries or liquid fuel
or other global power system issues.

A later white paper will discuss the use of propulsive forces other
than foot contacts, as well as additional actuation at the contacts (air
bags, springs, other ways to rapidly apply stored energy) for
operator safety (dodging threats, ...) and high performance (jumping, ...).

A future white paper will discuss near term soft robotics technology
for exoskeletons.

A future white paper could discuss the addition of extra limbs to an
exoskeleton~\cite{IEEE07139896}.

@@

\section{What are the specs?}

Hip, knee, ankle: At least 100Nm, more is better.

\subsection{What speeds and forces are needed to walk?}

\subsection{What speeds and forces are needed to run?}

\subsection{What operator-exoskeleton contact forces are acceptable?}

@@

Survey state of the art using linear electric actuators (typically ballscrews):
Roboray (Samsung)

>>>>

@@

\title{A Survey of Near-Term Exoskeleton Technology\\
(Draft 3.0)}

@@

This paper surveys near-term exoskeleton technology with an
emphasis on control.
A companion paper surveys implemented exoskeleton technology [survey.pdf].

@@

We do not survey exoskeleton technology for human arms. 
We treat the torso and helmet of the exoskeleton as the payload,
and focus on a lower body exoskeleton to support any payloads that
are on the torso or head.

We do not cover global energy storage such as batteries or liquid fuel
or other global power system issues.

A later white paper could discuss the use of propulsive forces other
than foot contacts, as well as additional actuation at the contacts (air
bags, springs, other ways to rapidly apply stored energy) for
operator safety (dodging threats, ...) and high performance (jumping, ...).

A future white paper could discuss near term soft robotics technology
for exoskeletons.

A future white paper could discuss the addition of extra limbs and
other effectors to an exoskeleton~\cite{IEEE07139896}.

@@

@@

Survey state of the art using linear electric actuators (typically ballscrews):
RoboKnee, Roboray (Samsung)
